Refinements for open automata

### 2022-02-09 2021-Refinement/paper/refinementarticle.tex
encore un pas preuve...

\item We need to prove for any OT $t_{13}$ in $T_{13}$ originating from $s_{13}$:
\begin{align*}
		&  \OTx{13}{}{13}{13} \in \fOT{s_{13}}
\end{align*}		
there exists an indexed family $t_{23x}$ of OTs originating from $s_{23}$: 
\begin{align*}
		&  \mpar{\OTx{23}{x}{23x}{23x} \in \fOT{s_{23}}}^{x \in X}
\end{align*}	
\begin{align*}		
		& \text{such that } \mpar{\forall x \in X, J'_{23x} \cap H' = J'_{13} \cap H'} \text{ and }\\
		&  V_{13} \uplus V_{23} \uplus \fvars{t_{13}} \vdash R'\mpar{s_{13}, s_{23}} \wedge g_{13} \implies \operatorname*{\bigsymb{\bigvee}}_{x \in X} \mpar{\everymath{\displaystyle}\begin{array}{l}
			\alpha_{13} = \alpha_{23x} \wedge \bigwedge_\subbox{j \in J'_{23x} \cap H'} \beta_{13j} = \beta_{23xj} \\[12pt]
			\nwedge g_{23x} \wedge R'\mpar{s'_{13}, s'_{23x}}\psubst{\psi_{13} \uplus \psi_{23x}}
		\end{array}} 
	\end{align*}
Recall that 
\begin{align*}
&V_{13}= V_1\uplus V^1_3 \text{ and }
V_{23}= V_2\uplus V^2_3\\
& H' \subseteq J_3\uplus \mpar{J_1 \cap J_2} \setminus \{k\} = \mpar{J_3\uplus J_1 \setminus \{k\} } \cap \mpar{J_3\uplus J_2 \setminus \{k\}} \\
\end{align*}

@@

For all $x \in X$ we have to consider both  cases:
\begin{align*}
	\text{if } k \in J'_1:\quad &  J'_{23x} \cap H'  
=((J'_{2x}  \setminus \mbrc{k})\uplus J^{2 \prime}_{3} ) \cap (H\uplus J_3 \setminus\{k\} )\\
&=((J'_{2x}\cap (H\uplus J_3))\uplus (J^{2 \prime}_{3}\cap (H\uplus J_3)))\setminus \mbrc{k}\\
&=((J'_{2x}\cap H)\uplus (J^{2 \prime}_{3}\cap  J_3))\setminus \mbrc{k}\text{ since } J_3\cap J'_{2x} = \emptyset \text{ and } H\cap J^{2 \prime}_{3} = \emptyset\\
& =((J'_{2x}\cap H)\uplus J^{2 \prime}_{3})\setminus \mbrc{k}\text{ since } J^{2 \prime}_{3}\subseteq J_3\\
& =(J'_1\cap H)\uplus J^{1 \prime}_{3}\setminus \mbrc{k}\quad \text{ since } J^{1 \prime}_{3}=J^{2 \prime}_{3} \text{ and } J'_1 \cap H = J'_{2x} \cap H\\
&= ((J'_1 \cap H) \uplus (J^{1 \prime}_{3} \cap J_3)) \setminus \mbrc{k}\text{ since } J^{1 \prime}_{3}\subseteq J_3\\ 
& = (J'_1\cap (J_3 \uplus H)) \uplus ((J^{1 \prime}_{3} \cap (J_3 \uplus H)) \setminus \mbrc{k} \text{ since } J_3\cap J'_{1} = \emptyset \text{ and } H\cap J^{1 \prime}_{3} = \emptyset\\
		& = \mpar{(J'_1  \uplus J^{1 \prime}_{3})\setminus \mbrc{k}} \cap \mpar{(J_{3} \uplus H) \setminus \mbrc{k}}\\
		& = J'_{13} \cap H'\\
\text{if } k \notin J'_1:\quad &	J'_{23x} \cap H'  = \mpar{J'_{2x} } \cap \mpar{J_3 \uplus H \setminus \mbrc{k}} \\
& = \mpar{J'_{2x}\cap H } \text{ since } J'_{2x}\cap J_3=\emptyset \land k\not\in J'_{2x} \\
& = \mpar{J'_1\cap H }\\
& = \mpar{J'_{13}\cap H' } \text{ since } J_3\cap J'_1=\emptyset \land k\not\in J_1'\\
\end{align*}

For the rest of the formula we will also consider the two cases separately.

\begin{itemize}
\item If $k \in J'_1$: we will extend the valuation context of the variables to cover the variables of the transition $t_3$. Based on this fact we have: $ \alpha_{1} = \alpha_{2x} \Rightarrow \alpha_{13} = \alpha_{23x}$ because composition doesn't change the resulting actions, nor their variables. 
We also have 
${\displaystyle \bigwedge_\subbox{j \in J'_{23x} \cap H} \beta_{1j} = \beta_{2xj} \Rightarrow  \bigwedge_\subbox{j \in J'_{23x} \cap H} \beta_{13j} = \beta_{23xj}}$ since the actions of the holes in $J_3$ coincide on both sides. And the following statements: 
$g_{13} \Leftrightarrow g_1 \wedge g_3 \wedge \alpha_3=\beta_{1k}$, 
$g_{23x}  \Leftrightarrow g_{2x} \wedge g_3 \wedge \alpha_3=\beta_{2xk}$ and $\beta_{1k} = \beta_{2xk}$\\

@@

From the formula $(*)$ to which we have added the same terms ($g_3 \wedge \alpha_3=\beta_{1k} {\displaystyle \wedge\bigwedge_\subbox{v_3\in V_3}  v^1_3=v^2_3\wedge s^1_3=s^2_3}$) to both sides of the implication and from all the points mentioned above, we get:
\begin{multline*}
\bigforall V_1 \uplus  V_2  \uplus V_3 \uplus  \fvars{t_1} \uplus \fvars{t_3}\\
\bigexists \mpar{\fvars{\alpha_{13}}  \cup\!\!\! \bigcup_{j \in J'_{23x}} \!\!\!\fvars{\beta_{13j} } } \setminus  \mpar{V_1 \uplus  V_2  \uplus V_3 \uplus  \fvars{t_1} \uplus \fvars{t_3}}\\
R\mpar{s_1, s_{2}} \wedge g_1 \wedge g_3 \wedge \alpha_3=\beta_{1k} \wedge \bigwedge_\subbox{v_3\in V_3}  v^1_3=v^2_3\wedge s^1_3=s^2_3\implies\\ \operatorname*{\bigsymb{\bigvee}}_{x \in X} \mpar{\everymath{\displaystyle}
\begin{array}{l}
			\alpha_{13} = \alpha_{23x} \wedge \bigwedge_\subbox{j \in J'_{2x} \cap H} \beta_{13j} = \beta_{23xj} \nwedge\\
			 g_{2x} \wedge R\mpar{s'_1, s'_{2x}}\psubst{\psi_1 \uplus \psi_{2x}}
		\end{array}}  \wedge g_3 \wedge \alpha_3=\beta_{2xk} \wedge \bigwedge_\subbox{v_3\in V_3}  v^1_3=v^2_3\wedge s'^1_3=s'^2_3
\end{multline*}	
That can be re-written as follows:
\begin{multline*}
R\mpar{s_1, s_{2}} \wedge g_{13}  \wedge \bigwedge_\subbox{v_3\in V_3}  v^1_3=v^2_3\wedge s^1_3=s^2_3\implies\\ \operatorname*{\bigsymb{\bigvee}}_{x \in X} \mpar{\everymath{\displaystyle}
\begin{array}{l}
			\alpha_{13} = \alpha_{23x} \wedge \bigwedge_\subbox{j \in J'_{2x} \cap H} \beta_{13j} = \beta_{23xj} \nwedge\\
			 g_{23x} \wedge R\mpar{s'_1, s'_{2x}}\psubst{\psi_1 \uplus \psi_{2x}}\wedge \bigwedge_\subbox{v_3\in V_3}  v^1_3=v^2_3\wedge s'^1_3=s'^2_3
		\end{array}}   
\end{multline*}

By hypothesis $\reach{A_{13}}\mpar{s_{13}}$ holds,  we then have according to the Definition \ref{Def:Reach} the following:
\[ \fvars{t_{13}} \vdash \left(\reach{A_{13}}\mpar{s_{13}} \wedge g_{13} \implies \reach{A_{13}}\mpar{s_{13}'}\psubst{\psi_{13}}\right) \]	
\end{itemize}

@@

 that gives,  according to Definition \ref{Def:CompOA}

The open transition $t_{13}$ is obtained by the composition of $t_1=\OTx{1}{}{1}{1}$ and $t_3=\OTx{3^1}{}{3}{3}$, that gives,  according to Definition \ref{Def:CompOA}, an open transition in one of the following forms:
% \[  \choice{
%	\OTx{1}{}{1}{1} \text{ and }  \OTx{3}{}{3}{3}
%	& \text{if } k \in J'_{1} \\
%	\OTx{1}{}{1}{1}	 & \text{otherwise}
%	} \]
\[
\choice{
\OT{\mpar{s_1, s^1_3}}{\mpar{s'_1, {s^1_3}'}}{\alpha_1}{\beta_j^{j \in J'_1 \uplus J'_3 \setminus \{k\}}}{g_1 \wedge g_3 \wedge \alpha_3 = \beta_{1k}}{\psi_1 \uplus \psi_3} & \text{ if } k \in J'_{1} \\
\OT{\mpar{s_1, s^1_3}}{\mpar{s'_1, s^1_3}}{\alpha_1}{\beta_j^{j \in J'_1}}{g_1}{\psi_1}& \text{otherwise}
}
\]

We have  $k \in H$ and $k \in J'_{1}$ then  we have $k \in J'_{2x}$.\\
By composing the family of OTs  $t_{2x}^{x\in X}$ originating from  $s_2$ with an open transition $t_3=\OTx{3}{}{3}{3} \in T_3$
%$t_3 =\OT{q_3}{q_3'}{\alpha_{3}'}{\beta_j^{j \in J''_{3}}}{g_{3}'}{\psi_{3}'} \in T_3$ %${\OT{q_{3}}{q'_{3}}{\alpha_{3}}{\beta_{ j}^{j \in J'_{3}}}{g_{3}}{\psi_{3}}}$, 
gives a family of OTs $t_{23x}^{x\in X}$.  The result of the composition will be as follows:
\begin{enumerate}
\item if $ s^1_3=s^2_3$
\[
\choice{
\OT{\mpar{s_2, s^2_3}}{\mpar{s'_{2x}, {s^2_3}'}}{\alpha_{2x}}{\beta_j^{j \in J'_{2x} \uplus J'_3 \setminus \{k\}}}{g_{2x} \wedge g_3 \wedge \alpha_3 = \beta_{2xk}}{\psi_{2x} \uplus \psi_3} & \text{ if } k \in J'_{2x} \\
\OT{\mpar{s_2, s^2_3}}{\mpar{s'_{2x}, s^2_3}}{\alpha_{2x}}{\beta_j^{j \in J'_{2x}}}{g_{2x}}{\psi_{2x}}& \text{otherwise}
}
\]
\item if $s^1_3 \neq s^2_3$ no element is produced that results an empty family.
\end{enumerate}

It remains to prove that we have:
\begin{align*}		
		&\mpar{\forall x \in X, J'_{23x} \cap H' = J'_{13} \cap H'} \text{ and }\\
		&  V_{13} \uplus V_{23} \uplus \fvars{t_{13}} \vdash R'\mpar{s_{13}, s_{23}} \wedge g_{13} \implies \operatorname*{\bigsymb{\bigvee}}_{x \in X} \mpar{\everymath{\displaystyle}\begin{array}{l}
			\alpha_{13} = \alpha_{23x} \wedge \bigwedge_\subbox{j \in J'_{23x} \cap H'} \beta_{13j} = \beta_{23xj} \\[12pt]
			\nwedge g_{23x} \wedge R'\mpar{s'_{13}, s'_{23x}}\psubst{\psi_{13} \uplus \psi_{23x}}
		\end{array}} 
	\end{align*}

For all $x \in X$ we have two cases:
\begin{align*}
		\text{if } k \in J'_1: && J'_{23x} \cap H' & = \mpar{J'_{3} \uplus J'_{2x} \setminus \mbrc{k}} \cap  \mpar{J'_{3} \uplus H \setminus \mbrc{k}}\\
		&&& = J'_{3}  \uplus \mpar{J'_{2x} \cap H} \setminus \mbrc{k} \\
		&&& = J'_{3} \uplus \mpar{J'_1 \cap H} \setminus \mbrc{k} \\
		&&& = \mpar{ J'_{3} \uplus J'_1 \setminus \mbrc{k}} \cap \mpar{J'_{3} \uplus H \setminus \mbrc{k}}\\
		&&& = J'_{13} \cap H'\\
\text{if } k \notin J'_1: && J'_{23x} \cap H' & = \mpar{J'_{2x} \setminus \mbrc{k}} \cap \mpar{J'_3 \uplus H \setminus \mbrc{k}} \\
		&&& = \mpar{J'_{2x} \cap H} \setminus \mbrc{k} \\
		&&& = \mpar{J'_1 \cap H} \setminus \mbrc{k}  \\
		&&& = J'_3 \uplus \mpar{J'_1 \cap H} \setminus \mbrc{k}  \\
		&&& = J'_{13} \cap H'
		\end{align*}

\smallskip

By adding the same terms to both sides of the implication of the  formula $(*)$, we get:

\begin{itemize}
\item In the case $ s^1_3=s^2_3$ and $k \in J'_1$:\\
$\displaystyle {\forall v \in \mpar{\fvars{\alpha_{1}}  \cup\!\!\! \bigcup_{j \in J'_{2x}} \!\!\!\fvars{\beta_{1j} } } \setminus  \mpar{V_1 \uplus  V_2 \uplus \fvars{t_1}}},$
\begin{multline*}
R\mpar{s_1, s_{2}} \wedge g_1 \wedge g_3 \wedge \alpha_3=\beta_{1k} \wedge s^1_3=s^2_3\implies\\ \operatorname*{\bigsymb{\bigvee}}_{x \in X} \mpar{\everymath{\displaystyle}
\begin{array}{l}
			\alpha_1 = \alpha_{2x} \wedge \bigwedge_\subbox{j \in J'_{2x} \cap H} \beta_{1j} = \beta_{2xj} \nwedge\\
			 g_{2x} \wedge R\mpar{s'_1, s'_{2x}}\psubst{\psi_1 \uplus \psi_{2x}}
		\end{array}}  \wedge g_3 \wedge \alpha_3=\beta_{1k} \wedge s^1_3=s^2_3
\end{multline*}	
Based on the fact that the composition doesn't change the resulting actions, nor the variables, and on the fact that for $k \in H$ we have $\beta_{1k}=\beta_{2xk}$, the we get after simplification:
\begin{multline*}
R\mpar{s_1, s_{2}} \wedge g_{13} \wedge s^1_3=s^2_3\implies\\ \operatorname*{\bigsymb{\bigvee}}_{x \in X} \mpar{\everymath{\displaystyle}
\begin{array}{l}
			\alpha_{13} = \alpha_{23x} \wedge \bigwedge_\subbox{j \in J'_{23x} \cap H} \beta_{1j} = \beta_{2xj} \nwedge\\
			 g_{2x} \wedge R\mpar{s'_1, s'_{2x}}\psubst{\psi_1 \uplus \psi_{2x}}
		\end{array}}  \wedge g_3 \wedge \alpha_3=\beta_{1k} \wedge s^1_3=s^2_3
\end{multline*}

By hypothesis $\reach{A_{13}}\mpar{s_{13}}$ holds,  we then have according to the Definition \ref{Def:Reach} the following:
\[ \fvars{t_{13}} \vdash \left(\reach{A_{13}}\mpar{s_{13}} \wedge g_{13} \implies \reach{A_{13}}\mpar{s_{13}'}\psubst{\psi_{13}}\right) \]	
\end{itemize}
\TODO{Pas termine: valider d'abord la definition de R}
\item The last formula to prove is the following:
\begin{multline*}
\forall \mpar{s_{13}, s_{23}} \in S_{13} \times S_{23},\\ V_{13} \uplus V_{23} \uplus \biguplus_\subbox{t_{23}\in \fOT{s_{23}}} \fvars{t_2} \vdash \left(R\mpar{s_{13}, s_{23}} \wedge \bigvee_\subbox{t_{23} \in \fOT{s_{23}}} \fguard{t_{23}} \implies \bigvee_\subbox{t_1 \in \fOT{s_{13}}} \fguard{t_{13}} \right)
\end{multline*}
By hypothesis we have the following:
\begin{multline*}
\forall \mpar{s_1, s_2} \in S_1 \times S_2,\\ V_1 \uplus V_2 \uplus \biguplus_\subbox{t_2 \in \fOT{s_2}} \fvars{t_2} \vdash \left(R\mpar{s_1, s_2} \wedge \bigvee_\subbox{t_2 \in \fOT{s_2}} \fguard{t_2} \implies \bigvee_\subbox{t_1 \in \fOT{s_1}} \fguard{t_1} \right)
\end{multline*}
By adding the term $\displaystyle{\bigvee_\subbox{t_3 \in \fOT{s_3}} \fguard{t_3}}$ to both sides of the implication, we get: 
\begin{multline*}
\forall \mpar{s_1, s_2,s_3} \in S_1 \times S_2 \times S_3, V_1 \uplus V_2 \uplus \biguplus_\subbox{t_2 \in \fOT{s_2}} \fvars{t_2} \vdash\\ \left(R\mpar{s_1, s_2} \wedge \bigvee_\subbox{t_2 \in \fOT{s_2}} \fguard{t_2} \wedge \bigvee_\subbox{t_3 \in \fOT{s_3}} \fguard{t_3} \implies \bigvee_\subbox{t_1 \in \fOT{s_1}} \fguard{t_1} \wedge \bigvee_\subbox{t_3 \in \fOT{s_3}} \fguard{t_3}\right)
\end{multline*}
By hypothesis we also have \(A_1\subst{A_3}{k}\) is non-blocking,  thus we can write the following:
\[ \fvars{t_{13}} \vdash \left(\reach{A_{13}}\mpar{s_{13}} \wedge g_{13} \implies \reach{A_{13}}\mpar{s_{13}'}\psubst{\psi_{13}}\right) \]	
\end{enumerate}

>>>>

\item We need to prove for any OT $t_{13}$ in $T_{13}$ originating from $s_{13}$:
\begin{align*}
		&  \OTx{13}{}{13}{13} \in \fOT{s_{13}}
\end{align*}		
there exists an indexed family $t_{23x}$ of OTs originating from $s_{23}$: 
\begin{align*}
		&  \mpar{\OTx{23}{x}{23x}{23x} \in \fOT{s_{23}}}^{x \in X}
\end{align*}	
\begin{align*}		
		& \text{such that } \mpar{\forall x \in X, J'_{23x} \cap H' = J'_{13} \cap H'} \text{ and }\\
		&  V_{13} \uplus V_{23} \uplus \fvars{t_{13}} \vdash R'\mpar{s_{13}, s_{23}} \wedge g_{13} \implies \operatorname*{\bigsymb{\bigvee}}_{x \in X} \mpar{\everymath{\displaystyle}\begin{array}{l}
			\alpha_{13} = \alpha_{23x} \wedge \bigwedge_\subbox{j \in J'_{23x} \cap H'} \beta_{13j} = \beta_{23xj} \wedge\\[12pt]
			 g_{23x} \wedge R'\mpar{s'_{13}, s'_{23x}}\psubst{\psi_{13} \uplus \psi_{23x}}
		\end{array}} 
	\end{align*}
Recall that 
\begin{align*}
&V_{13}= V_1\uplus V^1_3 \text{ and }
V_{23}= V_2\uplus V^2_3\\
& H' \subseteq J_3\uplus \mpar{J_1 \cap J_2} \setminus \{k\} = \mpar{J_3\uplus J_1 \setminus \{k\} } \cap \mpar{J_3\uplus J_2 \setminus \{k\}} \\
\end{align*}

@@

For all $x \in X$ we have to consider both  cases:
\begin{align*}
	\text{if } k \in J'_1:\quad &  J'_{23x} \cap H'  
=((J'_{2x}  \setminus \mbrc{k})\uplus J^{2 \prime}_{3} ) \cap (H\uplus J_3 \setminus\{k\} )\\
&=((J'_{2x}\cap (H\uplus J_3))\uplus (J^{2 \prime}_{3}\cap (H\uplus J_3)))\setminus \mbrc{k}\\
&=((J'_{2x}\cap H)\uplus (J^{2 \prime}_{3}\cap  J_3))\setminus \mbrc{k}\text{ since } J_3\cap J'_{2x} = \emptyset \text{ and } H\cap J^{2 \prime}_{3} = \emptyset\\
& =((J'_{2x}\cap H)\uplus J^{2 \prime}_{3})\setminus \mbrc{k}\text{ since } J^{2 \prime}_{3}\subseteq J_3\\
& =(J'_1\cap H)\uplus J^{1 \prime}_{3}\setminus \mbrc{k}\quad \text{ since } J^{1 \prime}_{3}=J^{2 \prime}_{3} \text{ and } J'_1 \cap H = J'_{2x} \cap H\\
&= ((J'_1 \cap H) \uplus (J^{1 \prime}_{3} \cap J_3)) \setminus \mbrc{k}\text{ since } J^{1 \prime}_{3}\subseteq J_3\\ 
& = (J'_1\cap (J_3 \uplus H)) \uplus ((J^{1 \prime}_{3} \cap (J_3 \uplus H)) \setminus \mbrc{k} \text{ since } J_3\cap J'_{1} = \emptyset \text{ and } H\cap J^{1 \prime}_{3} = \emptyset\\
		& = \mpar{(J'_1  \uplus J^{1 \prime}_{3})\setminus \mbrc{k}} \cap \mpar{(J_{3} \uplus H) \setminus \mbrc{k}}\\
		& = J'_{13} \cap H'\\
\text{if } k \notin J'_1:\quad &	J'_{23x} \cap H'  = \mpar{J'_{2x} } \cap \mpar{J_3 \uplus H \setminus \mbrc{k}} \\
& = \mpar{J'_{2x}\cap H } \text{ since } J'_{2x}\cap J_3=\emptyset \land k\not\in J'_{2x} \\
& = \mpar{J'_1\cap H }\\
& = \mpar{J'_{13}\cap H' } \text{ since } J_3\cap J'_1=\emptyset \land k\not\in J_1'\\
\end{align*}
For the rest of the formula we will also consider the two cases separately. 
\begin{itemize}
\item if $k \in J'_1$:\\
Because composition doesn't change the resulting actions, nor their variables, we can extend the valuation context of the variables to cover the variables of the transition $t_3$, we will then have:\\ $ \alpha_{1} = \alpha_{2x} \Rightarrow \alpha_{13} = \alpha_{23x}$ and
${\displaystyle \bigwedge_\subbox{j \in J'_{23x} \cap H} \beta_{1j} = \beta_{2xj} \Rightarrow  \bigwedge_\subbox{j \in (J'_{2x} \cap H)\uplus J_3} \beta_{13j} = \beta_{23xj}}$\\
On another side,   the composition gives $g_{13} \Leftrightarrow g_1 \wedge g^1_3 \wedge \alpha^1_3=\beta_{1k}$ and
$g_{23x}  \Leftrightarrow g_{2x} \wedge g^2_3 \wedge \alpha^2_3=\beta_{2xk}$. \\
In addition $k \in H$ we have   
$\beta_{1k} = \beta_{2xk}$ then we  deduce:
$g^1_3 \wedge \alpha^1_3=\beta_{1k}  \Leftrightarrow g^2_3 \wedge \alpha^2_3= \beta_{2xk}$

@@

By adding the same (and equivalent) terms  to both sides of the implication of the formula $(*)$,  and  from all the implications induced by the extension of the valuation context mentioned above, we get:
\begin{multline*}
V_1 \uplus V_2 \uplus \fvars{t_1} \uplus V^1_3  \uplus V^2_3 \vdash\\
R\mpar{s_1, s_{2}} \wedge g_1 \wedge g^1_3 \wedge \alpha^1_3=\beta_{1k} %\wedge \bigwedge_\subbox{v_3\in V_3}  v^1_3=v^2_3\wedge s^1_3=s^2_3
\implies  \hspace{12em}\\
\operatorname*{\bigsymb{\bigvee}}_{x \in X} \mpar{\everymath{\displaystyle}
\begin{array}{l}
			\alpha_{13} = \alpha_{23x} \wedge \bigwedge_\subbox{j \in (J'_{2x} \cap H)\uplus J_3} \beta_{13j}\! =\! \beta_{23xj}\\
			 \nwedge g_{2x} \wedge R\mpar{s'_1, s'_{2x}}\psubst{\psi_1 \uplus \psi_{2x}}
		\end{array}}  \wedge g^2_3 \wedge \alpha^2_3=\beta_{2xk} 
%\wedge \bigwedge_\subbox{v_3\in V_3}  v^1_3=v^2_3\wedge s^1_3=s^2_3
\end{multline*}	
That can be re-written as follows:
\begin{multline*}
V_{13} \uplus V_{23} \uplus \fvars{t_1}  \vdash\\
R\mpar{s_1, s_{2}} \wedge g_{13}  
%\wedge \bigwedge_\subbox{v_3\in V_3}  v^1_3=v^2_3\wedge s^1_3=s^2_3
\implies  \operatorname*{\bigsymb{\bigvee}}_{x \in X} \mpar{\everymath{\displaystyle}
\begin{array}{l}
			\alpha_{13} = \alpha_{23x} \wedge \bigwedge_\subbox{j \in J'_{23x} \cap H'} \beta_{13j} = \beta_{23xj} \\
			\nwedge g_{23x} \wedge R\mpar{s'_1, s'_{2x}}\psubst{\psi_1 \uplus \psi_{2x}}
%\wedge \bigwedge_\subbox{v_3\in V_3}  v^1_3=v^2_3\wedge s^1_3=s^2_3
		\end{array}}   
\end{multline*}

By hypothesis we have  \(A_1\subst{A_3}{k}\) is non-blocking,  then according to the Definition \ref{Def:Reach} we have $ \sigma_{013} \vdash \reach{A_{13}}\mpar{s_{013}}$ and for all $t_{13} \in T_{13}$:
\[ \fvars{t_{13}} \vdash \left(\reach{A_{13}}\mpar{s_{13}} \wedge g_{13} \implies \reach{A_{13}}\mpar{s_{13}'}\psubst{\psi_{13}}\right) \]	
From these two previous formulas we obtain:
\begin{multline*}
V_{13} \uplus V_{23} \uplus \fvars{t_1}  \uplus \fvars{t_{13}} \vdash\\
R\mpar{s_1, s_{2}} \wedge g_{13}  \wedge \reach{A_{13}}\mpar{s_{13}}
%\wedge \bigwedge_\subbox{v_3\in V_3}  v^1_3=v^2_3\wedge s^1_3=s^2_3
\implies  \operatorname*{\bigsymb{\bigvee}}_{x \in X} \mpar{\everymath{\displaystyle}
\begin{array}{l}
			\alpha_{13} = \alpha_{23x} \wedge \bigwedge_\subbox{j \in J'_{23x} \cap H'} \beta_{13j} = \beta_{23xj} \\
			\nwedge g_{23x} \wedge R\mpar{s'_1, s'_{2x}}\psubst{\psi_1 \uplus \psi_{2x}} 
%\wedge \bigwedge_\subbox{v_3\in V_3}  v^1_3=v^2_3\wedge s^1_3=s^2_3
		\end{array}}   \wedge \reach{A_{13}}\mpar{s_{13}'}\psubst{\psi_{13}} 
\end{multline*}

Considering that ate each step the valuations $\sigma_{3}^1$ and $\sigma_{3}^2$ associate the same values to the ``same'' variables modulo renaming, we have the tautology:\\ $\left({\displaystyle \bigwedge_\subbox{v_3\in V_3} v^1_3=v^2_3\wedge s^1_3 = s^2_3}\right)\psubst{\sigma_{3}^1 \uplus \sigma_{3}^2 }$.

\end{itemize}

@@

\TODO{Pas termine: valider d'abord la definition de R}
\item The last formula to prove is the following:
\begin{multline*}
\forall \mpar{s_{13}, s_{23}} \in S_{13} \times S_{23},\\ V_{13} \uplus V_{23} \uplus \biguplus_\subbox{t_{23}\in \fOT{s_{23}}} \fvars{t_2} \vdash \left(R\mpar{s_{13}, s_{23}} \wedge \bigvee_\subbox{t_{23} \in \fOT{s_{23}}} \fguard{t_{23}} \implies \bigvee_\subbox{t_1 \in \fOT{s_{13}}} \fguard{t_{13}} \right)
\end{multline*}
By hypothesis we have the following:
\begin{multline*}
\forall \mpar{s_1, s_2} \in S_1 \times S_2,\\ V_1 \uplus V_2 \uplus \biguplus_\subbox{t_2 \in \fOT{s_2}} \fvars{t_2} \vdash \left(R\mpar{s_1, s_2} \wedge \bigvee_\subbox{t_2 \in \fOT{s_2}} \fguard{t_2} \implies \bigvee_\subbox{t_1 \in \fOT{s_1}} \fguard{t_1} \right)
\end{multline*}
By adding the term $\displaystyle{\bigvee_\subbox{t_3 \in \fOT{s_3}} \fguard{t_3}}$ to both sides of the implication, we get: 
\begin{multline*}
\forall \mpar{s_1, s_2,s_3} \in S_1 \times S_2 \times S_3, V_1 \uplus V_2 \uplus \biguplus_\subbox{t_2 \in \fOT{s_2}} \fvars{t_2} \vdash\\ \left(R\mpar{s_1, s_2} \wedge \bigvee_\subbox{t_2 \in \fOT{s_2}} \fguard{t_2} \wedge \bigvee_\subbox{t_3 \in \fOT{s_3}} \fguard{t_3} \implies \bigvee_\subbox{t_1 \in \fOT{s_1}} \fguard{t_1} \wedge \bigvee_\subbox{t_3 \in \fOT{s_3}} \fguard{t_3}\right)
\end{multline*}
By hypothesis we also have \(A_1\subst{A_3}{k}\) is non-blocking,  thus we can write the following:
\[ \fvars{t_{13}} \vdash \left(\reach{A_{13}}\mpar{s_{13}} \wedge g_{13} \implies \reach{A_{13}}\mpar{s_{13}'}\psubst{\psi_{13}}\right) \]	
\end{enumerate}
